workshop

### 2023-02-21 scripts/workshop/workshop.Rmd
add ridgeplot

library(reshape2)
```

@@

incidence %>% ggplot(.,aes(x=Month.1, y=incidence)) + geom_col() + facet_grid(vars(WetAltID))
incidence %>% ggplot(.,aes(x=Month.1, y=incidence, group = 1)) + geom_point() + geom_line() + facet_wrap(~WetAltID, nrow = 5, ncol = 4) + labs(title="Incidence over time")
```

>>>>

library(reshape2)
library(ggridges)
```

@@

incidence %>% ggplot(.,aes(x=Month.1, y=incidence)) + geom_col() + facet_grid(vars(WetAltID))
incidence %>% ggplot(.,aes(x=Month.1, y=incidence, group = 1)) + geom_point() + geom_line() + 
  facet_wrap(~WetAltID, nrow = 5, ncol = 4) + labs(title="Incidence over time") + theme(axis.text.x = element_text(angle = 75, vjust = 0.5, hjust=1))

data %>% filter(RV.Status==1) %>% 
  ggplot(., aes(x=Month.1,
                y=WetAltID,
                group=WetAltID,
                fill=as.factor(WetAltID))) + 
  geom_density_ridges_gradient(show.legend=F) +
  labs(title="# of RV cases per site over time")

incidence %>% ggplot(., aes(x=Month.1,
                            y=WetAltID,
                            group=WetAltID,
                            fill=as.factor(WetAltID),
                            height = incidence)) +
  geom_density_ridges_gradient(show.legend = F, stat = "identity")
```
